IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/conclusion.tex
nit on conclusions

We present a formal semantics which describes how to extend arbitrary languages
with language-based coarse-grained IFC. We provably show the security guarantees
TSNI and TINI non-interference, where the proof technique is parametrized on the
target language, and it is developed for two ubiquitous scheduling policies. In
addition, we provide conditions to securely refine our formal semantics to
consider optimizations required in practice. Finally, we describe extensions to
the core IFC language with more advanced concepts like labeled values, privileges,
and a notation of clearance, and therefore connecting it with existing
IFC implementations for Javascript, Haskell, and (in
less detail) proposing IFC for C.

With this work, we set a global framework which describes how ideas from
OS can be systematically applied in programming languages.

>>>>

We present a formal semantics which describes how to extend arbitrary languages
with language-based coarse-grained IFC. We provably show the security guarantees
TSNI and TINI non-interference, where the proof technique is parametrized on the
target language, and it is developed for two ubiquitous scheduling policies. In
addition, we provide conditions to securely refine our formal semantics to
consider optimizations often required in practice. Finally, we describe
extensions to the core IFC language with more advanced concepts like labeled
values, privileges, and a notation of clearance, which allows us to draw
connections to existing IFC implementations for Javascript, Haskell, and (in
less detail) proposing IFC for C. With this work, we aim to expose how ideas
from IFC in OS can be systematically applied in programming languages.
